Approximation as Differentiation

### 2025-06-18 main/first-order.tex
Correction.
Tweak.

To say that a category $\cat{C}$ is enriched in $\CMon$, the (monoidal) category of commutative monoids, is to
say that every hom-set $\cat{C}(X,Y)$ provides an operation + to add morphisms together plus a zero morphism
$0: X \to Y$, and moreover that composition is \emph{bilinear}, i.e.~given by a family of morphisms
$\Hom{\cat{C}}{Y}{Z} \tensor \Hom{\cat{C}}{X}{Y} \to \Hom{\cat{C}}{X}{Z}$ in $\CMon$ that preserve the
additive structure in $\Hom{\cat{C}}{Y}{Z}$ and $\Hom{\cat{C}}{X}{Y}$ separately:

@@

\begin{proposition}
\label{prop:biproducts:from-product-or-coproduct}
In any $\CMon$-category:
\begin{enumerate}
\item If $X \times Y$ is a product then it is also coproduct, with $\inj_X = \prodM{\id}{0}$ and $\inj_Y =
\prodM{0}{\id}$.
\item If $X \coprod Y$ is a coproduct then it is also a product, with $\pi_1 = \coprodM{\id}{0}$ and $\pi_2 =
\coprodM{0}{\id}$.
\item $X$ is terminal iff it is initial.
\end{enumerate}
\end{proposition}

>>>>

A category $\cat{C}$ is enriched in $\CMon$, the (monoidal) category of commutative monoids, if every hom-set
$\cat{C}(X,Y)$ provides an operation + to add morphisms together, as well as a zero morphism $0: X \to Y$, and
composition is \emph{bilinear}, i.e.~given by a family of morphisms $\Hom{\cat{C}}{Y}{Z} \tensor
\Hom{\cat{C}}{X}{Y} \to \Hom{\cat{C}}{X}{Z}$ in $\CMon$ that preserve the additive structure in
$\Hom{\cat{C}}{Y}{Z}$ and $\Hom{\cat{C}}{X}{Y}$ separately:

@@

\begin{proposition}
\label{prop:biproducts:from-product-or-coproduct}
In any $\CMon$-category:
\begin{enumerate}
\item If $X \times Y$ is a product then it is also coproduct, with $\inj_1 = \prodM{\id}{0}$ and $\inj_2 =
\prodM{0}{\id}$.
\item If $X \coprod Y$ is a coproduct then it is also a product, with $\pi_1 = \coprodM{\id}{0}$ and $\pi_2 =
\coprodM{0}{\id}$.
\item $X$ is terminal iff it is initial.
\end{enumerate}
\end{proposition}
